### 2017-04-14 paper/oopsla17-submission/evaluation.tex
done with overview
shuffle

\input{evaluation-accuracy}
\input{evaluation-utility}
\input{gallery}

\subsection{Threats to Validity}

Although our experiments demonstrate that our technique can pinpoint type
errors more accurately than the state of the art and that our features are
relevant to blame assignment, our results may not generalize.

One threat to validity associated with supervised machine learning is
overfitting (\ie learning a model that is too complex with respect to
the data).
%
We mitigate this threat by having separate training and testing datasets
(\autoref{sec:quantitative}) and via cross-validation
(\autoref{sec:feature-utility})~\cite{FIXME}.

Our benchmarks were drawn from students in an undergraduate course and
may not be representative of other student populations.
%
We mitigate this threat by including the largest empirical evaluation of
type error localization that we are aware of: over 4,500 pairs of
ill-typed programs and fixes from two instances of the course, with
programs from 102 different students.
%
We acknowledge, of course, that students are not industrial programmers
and our results may not translate to large-scale software development;
however, we are particularly interested in aiding novice programmers
as they learn to work inside the type system.

A related threat to construct validity is our definition of the immedate
next well-typed program as the intended ground truth answer (see
\autoref{sec:overview}, Challenge 2). Students may, in theory, submit
intermediate well-typed program ``rewrites'' between the original ill-typed
program and the final intended answer. Our approach to discarding outliers
(see \autoref{sec:evaluation}) is designed to mitigate this threat.

Our removal of program pairs that changed too much, where our oracle
could not identify the blame of the other tools, or where the other
tools timed out or encountered unsupported language features is another
threat to validity.
%
It is possible that including the programs that changed excessively
would hurt our models, or that the other tools would perform
better on the programs with unsupported language features.
%
We note however that
%
(1) outlier removal is a standard technique in machine learning
\ES{CITE?}; and
%
(2) our Top-1 accuracy margin is large enough that even if we assumed
that \sherrloc were perfect on all of the excluded programs, it would
only tie our \hiddenFH in Top-1 accuracy.
%
\ES{I think this is accurate, but should double check..}

Examining programs written in \ocaml as opposed to \haskell or any other
language poses another threat to validity, common type errors may differ
in different languages.
%
\ocaml is, however, a standard target for research in type error
localization and thus our choice admits a direct comparison with prior
work.
%
Furthermore, the functional core of \ocaml that we support does not
differ significantly from the functional core of \haskell or SML, all of
which are effectively lambda calculi with a Hindley-Milner-style type
system.\footnote{\haskell's type classes are a notable exception, they
  are also known to cause confusing type errors and would be interesting
  to study in future work.}

Finally, our use of student fixes as oracles for the source of type
errors assumes that, on average, students are able to correctly identify
the source of an error.
%
As the students are in the process of learning the language and type
system, this assumption may be faulty.
%
It may be that \emph{expert} users would disagree with many of the
student fixes, and that it is harder to learn a model of expert fixes,
or that the state of the art would be better at predicting expert fixes.
%
As we have noted before, we believe it is reasonable to use student
fixes as oracles because the student is the best judge of what she
\emph{meant} to do.

>>>>

\input{evaluation-accuracy}
\input{evaluation-utility}

### 2017-04-14 paper/oopsla17-submission/qualitative.tex
shuffle

We explain the predictions by analyzing the paths induced in
the decision tree by the features of the input programs.
\ES{TODO: EXPOUND!!}
%
% We will also attempt, for each program, to explain \emph{why} the
% Decision Tree made its prediction, by analyzing the paths induced
% by the programs.

>>>>

We explain the predictions by analyzing the paths induced in
the decision tree by the features of the input expressions.
%
Recall that each node in a decision tree contains a simple predicate of
the features, \eg ``is feature $v_j$ enabled?'', which determines
whether a sample will continue down the left or right subtree.
%
Thus, we can examine the predicates used and the values of the
corresponding features to explain \emph{why} our \dectree made its
prediction.
%
We will focus particularly on the enabled features, as they generally
provide more information than the disabled features.
%
Furthermore, each node is additionally labeled with the ratio of
``blamed'' vs ``not-blamed'' training expressions that passed through
it.
%
We can use this information to identify particularly important
decisions, \ie we consider a decision that changes the ratio to be more
interesting than a decision that does not.

%
% We will also attempt, for each program, to explain \emph{why} the
% Decision Tree made its prediction, by analyzing the paths induced
% by the programs.
